---
title: "Project Abstract"
author: "Yining Chen, Yufei Deng, Ziqing Ji"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Project Abstract}
  %\VignetteEngine{knitr::rmarkdown}
  %\UseRaw{}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>"
)
```

# Background and Motivation

Colorectal cancer (CRC) is the fourth common malignancy, representing 8.3% of all cancer diagnoses and 8.4% of all cancer deaths in the US. There are more than one million people living with CRC in the United States and 4.2% percent of all adults are expected to be diagnosed with CRC at some point during their lifetime

# Research Question

# Data Cleaning and Exploration

## Datasets used in our analysis

```{r}
library(bis620.final)
crc_sub |> head(5)
```

## Data Visualization


### Time Trend

Proportion of Intervention Types over Time

```{r}
plot_intervention_proportion_time()
```

### Number of Intervention Types over Time
```{r}
plot_intervention_count_time()
```

## Summary table & Sankey Diagram
```{r}
summarize_crc_table()
```



# Analysis



```{r}
# analysis(....)
```

# Interpretation and Conclusions
